Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-11 snapshot_system/failover.tex
Revisions
Reference fixes and revisions

In VC, each non-PDS file system block is associated with one VM while PDS file system blocks are
shared among VMs  (at most $V$ VMs). Thus, 
\[
V *N_1 *s  = pD  \frac{\delta} {\delta +1} \; \mbox{ and } \; 
V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V.
\]
For the VO approach, 
\[
V *N_o *s  = pD  V_o.
\]
Then
\[
N_1= \frac{pD \delta} {V s (\delta +1)},\; 
N_2 \leq \frac{pD } {s (\delta +1)}, \; 
\mbox{and} \; N_o = \frac{pD V_o } {s V}.
\]
Since each file block (with default size $s=64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.
Figure~\ref{fig-fsb-links} shows the number of VMs sharing by each file block.
In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
We can observe in Figure~\ref{fig-vm-links} that $N_1 +N_2 < N_o$. This is likely because the PDS FSBs tightly pack data used by many VMs, which decreases the overall number of FSBs required to backup a VM.
If  the backup for multiple VMs is conducted concurrently, there would be more
VMs shared  by each file block on average.

Figure~\ref{fig-fsb-links} shows the average number of VMs sharing a
filesystem block (FSB) as VMs are added. Though we don't expect the linear trend to continue indefinitely for
much larger datasets, it should continue to increase, which has important implications
on VM backup availability in the precense of failures. Below we show the
significant impact the number of links has on VM backup reliability.

\comments{%dropping block links bec. we don't use it elsewhere
\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig-vo-links}
\end{figure}
}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig-fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
                mark options=solid,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=No] {figures/vo_vm_links.txt};
		\addplot table[x=VMs,y=N1] {figures/vc_vm_links.txt};
                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links.txt};
                \addplot+[dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig-vm-links}
\end{figure}

The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig-fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

in our current testbed we have measured the average number of links per chunk
(Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
(Figure~\ref{fig-fsb-links}) in our dataset. For the complete dataset, we also
found the average number of links to PDS chunks, which was \~19 using a 2\%
PDS. From Figure~\ref{fig-fsb-links} you can see that as you add VMs, the
average number of links to a chunk increases linearly for our dataset. We
expect that this trend will level out with larger datasets, but should continue
to increase at a slower rate.  For the VC model, we have to consider both PDS
chunks and non-PDS chunks. In the VO model all data is shared, but in VC only
the PDS data is shared, but at a much higher rate. This gives a strong
advantage to VC, in that for a large percent of the data (95-99\%), there is
only one VM pointing to each non-PDS chunk. You can see the increase in
reliability in Figure~\ref{fig-vm-availability}.
}

Figure~\ref{fig-vm-availability} shows the reliability of VM backups as storage
nodes fail for different amounts of sharing of filesystem blocks in the index. We
show 5 and 20 for the VO and VC block links counts because those are what we
measured in our small dataset, and chose higher numbers to account for much
larger datasets. We chose to use a very optimistic setting for VO (20), and the
absolute worst case amount of sharing for VC in a 100 machine cluster with 25
VMs per machine (2500). Our results show that even the VC worst case provides
better VM reliability that VO. As you can see from the graph, even small
changes in the number of links to VO blocks has a significant impact on
reliability, while even a 50 times increase in the VC block link counts only
slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replicaton
for PDS blocks also signficantly increases the snapshot availability even when
a PDS file block is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig-pds-replication}
shows the advantages of increasing the replication factor for PDS blocks. the
numbers in the graph are only meant to be relative, as we assume higher PDS
block links than we have measured in our dataset (to account for a much larger
body of data). It is easy to see though that increasing the replication of just
the PDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

\begin{table}
    \begin{tabular}{|l|lll|}
    \hline
    \multirow{2}{*}{Nodes Failed}   & \multicolumn{3}{c|}{Availability(\%)}\\
                                    & $R=3$ & $R=4$ & $R=5$\\
    \hline
    1           &  100      & 100       & 100\\
    2           & 100       & 100       & 100\\
    3          & 99.999     & 100       & 100\\
    5          & 99.993     & 99.9999   & 99.999998\\
    10          & 99.926    & 99.995    & 99.999\\
    20          & 99.295    & 99.876    & 99.979\\
    \hline
    \end{tabular}
    \caption{Availability in a 100 machine cluster of a single FSB in the global data store with different replication factors}
    \label{tab:fsb-availability}
\end{table}

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={\small Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig-fsb-availability}
\end{figure}

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                \addlegendentry{$VC\,20$ (measured)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                \addlegendentry{$VC\,2500$ (worst-case)}
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                \addlegendentry{$VO\,5$ (measured)}
                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                \addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for
  varying degrees of block sharing (i.e. average number of VMs that use a
  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
  Graph shown for 100 machine cluster.
  }
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig-pds-replication}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig-pds-replication2}
\end{figure}

>>>>

In VC, each non-PDS file system block is associated with one VM while PDS file system blocks are
shared among VMs  (at most $V$ VMs). Thus, 
\[
V *N_1 *s  = pD  \frac{\delta} {\delta +1} \; \mbox{ and } \; 
V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V.
\]
For the VO approach, 
\[
V *N_o *s  = pD  V_o.
\]
Then
\[
N_1= \frac{pD \delta} {V s (\delta +1)},\; 
N_2 \leq \frac{pD } {s (\delta +1)}, \; 
\mbox{and} \; N_o = \frac{pD V_o } {s V}.
\]
Since each file block (with default size $s=64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.
Figure~\ref{fig:fsb-links} shows the number of VMs sharing by each file block.
In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
We can observe in Figure~\ref{fig:vm-links} that $N_1 +N_2 < N_o$. This is likely because the PDS FSBs tightly pack data used by many VMs, which decreases the overall number of FSBs required to backup a VM.
If  the backup for multiple VMs is conducted concurrently, there would be more
VMs shared  by each file block on average.

Figure~\ref{fig:fsb-links} shows the average number of VMs sharing a
filesystem block (FSB) as VMs are added. Though we don't expect the linear trend to continue indefinitely for
much larger datasets, it should continue to increase, which has important implications
on VM backup availability in the precense of failures. Below we show the
significant impact the number of links has on VM backup reliability.

\comments{%dropping block links bec. we don't use it elsewhere
\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig:vo-links}
\end{figure}
}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO FSB links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{VO, PDS in VC};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in a 2\% PDS for VC.}
  \label{fig:fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO VM links},
		xlabel={Number of VMs},
		ylabel={\small Avg. Num. FSBs used by VM},
                ymin=0,
                mark options=solid,
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=north west
		]
                \addplot table[x=VMs,y=No] {figures/vo_vm_links.txt};
		\addplot table[x=VMs,y=N1] {figures/vc_vm_links.txt};
                \addplot+[red,densely dashed] table[x=VMs,y=N2] {figures/vc_vm_links.txt};
                \addplot+[red,dotted,mark=none] table[x=VMs,y expr=\thisrow{N1}+\thisrow{N2}] {figures/vc_vm_links.txt};
                \legend{$N_o$, $N_1$, $N_2$, $N_1+N_2$};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of 64MB FSBs used by a single VM. For VC both the number of PDS and Non-PDS FSBs used are shown.}
  \label{fig:vm-links}
\end{figure}

The snapshot availability of is a VM is the likelyhood that
there is no  data loss for all its file blocks.
With replication degree $r$, the likelyhood of
a file block block is the probability that  
all of its replicas appear in $d$ failed machines. 
Namely, $\binom{d}{r}/ \binom{p}{r}$. This can be seen in Figure~\ref{fig:fsb-availability} for a 100 machine cluster for 3 different replication factors.

@@

in our current testbed we have measured the average number of links per chunk
(Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
(Figure~\ref{fig:fsb-links}) in our dataset. For the complete dataset, we also
found the average number of links to PDS chunks, which was \~19 using a 2\%
PDS. From Figure~\ref{fig:fsb-links} you can see that as you add VMs, the
average number of links to a chunk increases linearly for our dataset. We
expect that this trend will level out with larger datasets, but should continue
to increase at a slower rate.  For the VC model, we have to consider both PDS
chunks and non-PDS chunks. In the VO model all data is shared, but in VC only
the PDS data is shared, but at a much higher rate. This gives a strong
advantage to VC, in that for a large percent of the data (95-99\%), there is
only one VM pointing to each non-PDS chunk. You can see the increase in
reliability in Figure~\ref{fig:vm-availability}.
}

Figure~\ref{fig:vm-availability} shows the reliability of VM backups as storage
nodes fail for different amounts of sharing of filesystem blocks in the index. We
show 5 and 20 for the VO and VC block links counts because those are what we
measured in our small dataset, and chose higher numbers to account for much
larger datasets. We chose to use a very optimistic setting for VO (20), and the
absolute worst case amount of sharing for VC in a 100 machine cluster with 25
VMs per machine (2500). Our results show that even the VC worst case provides
better VM reliability that VO. As you can see from the graph, even small
changes in the number of links to VO blocks has a significant impact on
reliability, while even a 50 times increase in the VC block link counts only
slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <
N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replicaton
for PDS blocks also signficantly increases the snapshot availability even when
a PDS file block is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig:pds-replication}
shows the advantages of increasing the replication factor for PDS blocks. the
numbers in the graph are only meant to be relative, as we assume higher PDS
block links than we have measured in our dataset (to account for a much larger
body of data). It is easy to see though that increasing the replication of just
the PDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

\begin{table}
    \begin{tabular}{|l|lll|}
    \hline
    \multirow{2}{*}{Nodes Failed}   & \multicolumn{3}{c|}{Availability(\%)}\\
                                    & $R=3$ & $R=4$ & $R=5$\\
    \hline
    1           &  100      & 100       & 100\\
    2           & 100       & 100       & 100\\
    3          & 99.999     & 100       & 100\\
    5          & 99.993     & 99.9999   & 99.999998\\
    10          & 99.926    & 99.995    & 99.999\\
    20          & 99.295    & 99.876    & 99.979\\
    \hline
    \end{tabular}
    \caption{Availability in a 100 machine cluster of a single FSB with different replication factors}
    \label{tab:fsb-availability}
\end{table}

\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={FSB Availability},
            cycle list name=mline,
            xlabel={Number of Machines Failed},
            ylabel={\small Availability of Single FSB (\%)},
            extra y ticks={99.9}, %to add extra ticks
            mark options=solid,
            legend pos=south west,
            %legend columns=2,
            %legend style={
            %    at={(0.5,-0.2)},
            %anchor=north}
            ]
            \addplot table[x=NodesFailed,y=Availability5] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability4] {figures/fsb_availability.txt};
            \addplot table[x=NodesFailed,y=Availability3] {figures/fsb_availability.txt};
            \legend{$R=5$,$R=4$,$R=3$};
            \end{axis}
    \end{tikzpicture}
    \caption{Availability of Individual FSBs in 100 Machine Cluster with different replication factors.}
  \label{fig:fsb-availability}
\end{figure}

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
                cycle multi list={
                    mline\nextlist
                    [2 of]mmark*\nextlist
                },
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                %reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability.txt};
                \addlegendentry{$VC\,20$ (measured)}
                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability.txt};
                \addlegendentry{$VC\,2500$ (worst-case)}
                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability.txt};
                \addlegendentry{$VO\,5$ (measured)}
                \addplot table[x=NodesFailed,y=VO2]{figures/vm_availability.txt};
                \addlegendentry{$VO\,20$ (optimistic)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for
  varying degrees of block sharing (i.e. average number of VMs that use a
  block). Non-PDS replication fixed at 3 and PDS replication increased to 4.
  Graph shown for 100 machine cluster.
  }
  \label{fig:vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig:pds-replication}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		%extra y ticks={99.99}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot table[x=NodesFailed,y=VC1]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/cds_replication2.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/cds_replication2.txt};
                %\addplot table[x=NodesFailed,y=VC4]{figures/cds_replication2.txt};
                \legend{$R_C=3$,$R_C=4$,$R_C=5$}%,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 20)}
  \label{fig:pds-replication2}
\end{figure}

### 2013-07-11 snapshot_system/intro.tex
removed extensions from pdf includes, set default ext in main updated makefile to include all proper prereqs, added phony remake and bibtex targets.
Reference fixes and revisions

\section{Introduction}
In a cluster-based cloud environment,
% such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
%Backup  of virtual disks is relatively straightforward since
%these image files are stored as regular files from the external point of view,
%backing up VM's data is mainly done by taking snapshots of virtual disk images.
%A snapshot preserves the data of a VM's file system at a specific point in time. 
%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.
The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand. 
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
%(Figure~\ref{fig-traditional-arch})
can effectively identify and remove content duplicates among snapshots, 
but such a solution can be expensive. There is also a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

%\begin{figure}[htb]
%    \centering
%    \includegraphics[width=3in]{images/traditional-arch.pdf}
%    \label{fig-traditional-arch}
%    \caption{Traditional VM Backup System}
%\end{figure}

@@

%\begin{figure}[htb]
%    \centering
%    \includegraphics[width=3in]{images/colocated-arch.pdf}
%    \label{fig-colocated-arch}
%    \caption{Collocated VM Backup System}
%\end{figure}

@@

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{review} reviews background and related work.
Section~\ref{sec:framework}  discusses the  design options for snapshot backup with a VM-centric approach. 
Section~\ref{sec:model}  analyzes the benefit of our approach for fault isolation. 
Section~\ref{sec:arch}  describes our system architecture and implementation details.
%   the benefit of our approach for fault isolation. 
Section~\ref{exper} is our experimental evaluation that compare with the other approaches.
Section~\ref{conc}  concludes this paper.

>>>>

\section{Introduction}
In a cluster-based cloud environment,
% such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun},
each physical machine runs a number  of virtual machines as  instances of a guest operating system 
and their  virtual hard disks are represented as virtual disk image files in the host operating system.
%virtual disk image files (e.g. .vhd, .vmdk) in the host operating system.
%Backup  of virtual disks is relatively straightforward since
%these image files are stored as regular files from the external point of view,
%backing up VM's data is mainly done by taking snapshots of virtual disk images.
%A snapshot preserves the data of a VM's file system at a specific point in time. 
%VM snapshots can be  backed up  incrementally by comparing blocks from one version to another 
%and only the blocks that have changed from the previous version of snapshot will be saved~\cite{Clements2009,Vrable2009}. 
Frequent  snapshot backup of virtual disk images  can increase  the service reliability. 
For example, the Aliyun cloud, which is  the largest cloud service provider by Alibaba in China, 
automatically conducts  the backup of virtual disk images to all active users every day.
The cost of supporting a large number of concurrent backup streams is high
because of the huge storage demand. 
Using a separate  backup service with full deduplication support~\cite{venti02,bottleneck08}
%(Figure~\ref{fig:traditional-arch})
can effectively identify and remove content duplicates among snapshots, 
but such a solution can be expensive. There is also a large amount of 
network traffic to transfer  data from the host machines to the backup facility
before duplicates are removed.

%\begin{figure}[htb]
%    \centering
%    \includegraphics[width=3in]{images/traditional-arch}
%    \label{fig:traditional-arch}
%    \caption{Traditional VM Backup System}
%\end{figure}

@@

%\begin{figure}[htb]
%    \centering
%    \includegraphics[width=3in]{images/colocated-arch}
%    \label{fig:colocated-arch}
%    \caption{Collocated VM Backup System}
%\end{figure}

@@

%************** Paper sections summary
%THIS NEEDS MODIFICATION
The rest of this paper is organized as follows.
Section~\ref{review} reviews background and related work.
Section~\ref{sect:framework}  discusses the  design options for snapshot backup with a VM-centric approach. 
Section~\ref{sect:model}  analyzes the benefit of our approach for fault isolation. 
Section~\ref{sect:arch}  describes our system architecture and implementation details.
%   the benefit of our approach for fault isolation. 
Section~\ref{exper} is our experimental evaluation that compare with the other approaches.
Section~\ref{conc}  concludes this paper.
